
\begin{algorithm}
\caption{Construction Heuristic}\label{alg:heuristic}
\begin{algorithmic}[1]

\State Start with a tour that only contains the depot.
% smallest g value, Unexplored verticies
\State If the current target cannot visit every unvisited target, backtrack to the previous element in the tour.

\State Add an edge from the current target to the target with the smallest $g$ value such that the resulting graph has not already been created by this step.

\State If the remaining fuel on arrival is less than the cost to return to the depot, insert a refueling depot before the last element in the tour. If the tour is no longer valid, backtrack.

\State Repeat the previous three steps until all targets are part of the tour.

\State Add the depot onto the end of the tour.

\end{algorithmic}
\end{algorithm}

\noindent When traveling from $i$ to $j$:
\begin{align}
    %
    & t^a_j = \max(t^a_i + f_{ij}, t^s_j) \\
    %
    & y_j = y_i - (t^a_j - t^a_i) 
    \quad \forall\ i \in S', \ \forall\ j \in V' \\
    %
    & y_j = C - (t^a_j - t^a_i)
    \quad \forall\ i \in V'\backslash S' \ \forall\ j \in S'
    %
\end{align}

\noindent The function $g(i,j)$ is the edge weight of $i\in V'$ to $j\in S'$. $w$ is the weightings of each parameter in $g$ and is unique for each solution.
%
\begin{equation}
    g(i,j) =
    w_1 t^e_j +
    w_2 t^s_j +
    w_3 f_{ij} +
    w_4 f_{j0} +
    w_5 t^a_j +
    w_6 y_j
\end{equation}

\noindent Each solution has a unique value of $w$ which is optimized through genetic evolution. Solutions with smaller tour lengths have a greater chance to pass on their values of $w$.
